Study of Higgs plus single top production using events with a same sign dimuon at the Large Hadron Collider

### 2019-11-27 tesis_hiram/Chapter3/chapter3.tex
n

The analysis described in this chapter is a summary of the publication from the CMS collaboration using 35.9 fb$^{-1}$ of Run II data~\cite{th1}, the Monte Carlo simulations and event yields shown below and used in the analysis described in the next chapter are obtained from this publication.

>>>>

The analysis described in this chapter is a summary of the publication from the CMS collaboration using 35.9 fb$^{-1}$ of Run II data~\cite{th1}. Monte Carlo simulations and event yields shown below and used in the analysis described in the next chapter are obtained from this publication.
